Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-03-29 Paper/paper.tex
Update Appendix B

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.6}}

@@

\subsection{Hydrogen-ionizing emissivity}

@@

\subsection{Hydrogen photoionization rate}

@@

\section{Table of emissivities}
\label{sec:tables}

Table~\ref{tab:gamma} shows the LyC emissivities and the resultant
hydrogen photoionisation rate due to quasars down to magnitudes
$M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the curves
shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
photoionisation rate calculation assumes an HI column density given by
\citet{2012ApJ...746..125H}.  See Sections XX and XX for further
details.

@@

    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.}

@@

\begin{table*}
  \caption{LyC emissivities and the resultant hydrogen photoionisation
    rate due to quasars down to magnitudes $M_{1450}=-18$ and
    $M_{1450}=-21$.  These numbers describe the curves shown in
    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The photoionisation
    rate calculation assumes an HI column density given by
    \citet{2012ApJ...746..125H}.  See Sections XX and XX for further
    details.  \gk{Do we need another table for the emissivities from
      individual models?}}
  \label{tab:gamma}
  \begin{tabular}{ccccc}
    \hline
    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
    \hline
    0.0 & 5.090e--14 & 2.822e--14 & 1.383e+23 & 7.011e+22 \\
    0.1 & 7.036e--14 & 4.069e--14 & 2.231e+23 & 1.176e+23 \\
    0.2 & 9.461e--14 & 5.690e--14 & 3.419e+23 & 1.877e+23 \\
    0.3 & 1.248e--13 & 7.787e--14 & 5.019e+23 & 2.873e+23 \\
    0.4 & 1.614e--13 & 1.041e--13 & 7.098e+23 & 4.240e+23 \\
    0.5 & 2.051e--13 & 1.363e--13 & 9.717e+23 & 6.056e+23 \\
    0.6 & 2.566e--13 & 1.750e--13 & 1.293e+24 & 8.401e+23 \\
    0.7 & 3.164e--13 & 2.208e--13 & 1.676e+24 & 1.135e+24 \\
    0.8 & 3.845e--13 & 2.736e--13 & 2.124e+24 & 1.495e+24 \\
    0.9 & 4.605e--13 & 3.330e--13 & 2.636e+24 & 1.923e+24 \\
    1.0 & 5.433e--13 & 3.980e--13 & 3.208e+24 & 2.419e+24 \\
    1.1 & 6.309e--13 & 4.667e--13 & 3.835e+24 & 2.978e+24 \\
    1.2 & 7.207e--13 & 5.367e--13 & 4.507e+24 & 3.589e+24 \\
    1.3 & 8.092e--13 & 6.046e--13 & 5.216e+24 & 4.237e+24 \\
    1.4 & 8.931e--13 & 6.675e--13 & 5.946e+24 & 4.902e+24 \\
    1.5 & 9.715e--13 & 7.246e--13 & 6.684e+24 & 5.559e+24 \\
    1.6 & 1.037e--12 & 7.693e--13 & 7.414e+24 & 6.185e+24 \\
    1.7 & 1.087e--12 & 8.003e--13 & 8.117e+24 & 6.754e+24 \\
    1.8 & 1.131e--12 & 8.246e--13 & 8.779e+24 & 7.245e+24 \\
    1.9 & 1.163e--12 & 8.364e--13 & 9.384e+24 & 7.642e+24 \\
    2.0 & 1.183e--12 & 8.386e--13 & 9.917e+24 & 7.932e+24 \\
    2.1 & 1.195e--12 & 8.322e--13 & 1.037e+25 & 8.112e+24 \\
    2.2 & 1.194e--12 & 8.156e--13 & 1.073e+25 & 8.184e+24 \\
    2.3 & 1.187e--12 & 7.941e--13 & 1.099e+25 & 8.153e+24 \\
    2.4 & 1.168e--12 & 7.636e--13 & 1.115e+25 & 8.030e+24 \\
    2.5 & 1.145e--12 & 7.308e--13 & 1.121e+25 & 7.827e+24 \\
    2.6 & 1.112e--12 & 6.915e--13 & 1.118e+25 & 7.558e+24 \\
    2.7 & 1.075e--12 & 6.516e--13 & 1.105e+25 & 7.237e+24 \\
    2.8 & 1.031e--12 & 6.080e--13 & 1.085e+25 & 6.877e+24 \\
    2.9 & 9.835e--13 & 5.648e--13 & 1.057e+25 & 6.490e+24 \\
    3.0 & 9.319e--13 & 5.207e--13 & 1.022e+25 & 6.087e+24 \\
    3.1 & 8.780e--13 & 4.774e--13 & 9.824e+24 & 5.676e+24 \\
    3.2 & 8.227e--13 & 4.354e--13 & 9.385e+24 & 5.267e+24 \\
    3.3 & 7.658e--13 & 3.945e--13 & 8.914e+24 & 4.864e+24 \\
    3.4 & 7.102e--13 & 3.565e--13 & 8.422e+24 & 4.473e+24 \\
    3.5 & 6.545e--13 & 3.202e--13 & 7.916e+24 & 4.098e+24 \\
    3.6 & 6.006e--13 & 2.865e--13 & 7.406e+24 & 3.740e+24 \\
    3.7 & 5.487e--13 & 2.554e--13 & 6.898e+24 & 3.402e+24 \\
    3.8 & 4.988e--13 & 2.265e--13 & 6.399e+24 & 3.085e+24 \\
    3.9 & 4.521e--13 & 2.006e--13 & 5.912e+24 & 2.789e+24 \\
    4.0 & 4.082e--13 & 1.769e--13 & 5.443e+24 & 2.515e+24 \\
    4.1 & 3.671e--13 & 1.554e--13 & 4.993e+24 & 2.262e+24 \\
    4.2 & 3.295e--13 & 1.363e--13 & 4.566e+24 & 2.029e+24 \\
    4.3 & 2.948e--13 & 1.192e--13 & 4.163e+24 & 1.816e+24 \\
    4.4 & 2.630e--13 & 1.039e--13 & 3.784e+24 & 1.622e+24 \\
    4.5 & 2.342e--13 & 9.045e--14 & 3.431e+24 & 1.445e+24 \\
    4.6 & 2.081e--13 & 7.854e--14 & 3.102e+24 & 1.286e+24 \\
    4.7 & 1.845e--13 & 6.803e--14 & 2.798e+24 & 1.141e+24 \\
    4.8 & 1.633e--13 & 5.883e--14 & 2.518e+24 & 1.011e+24 \\
    4.9 & 1.444e--13 & 5.078e--14 & 2.262e+24 & 8.944e+23 \\
    5.0 & 1.274e--13 & 4.373e--14 & 2.027e+24 & 7.898e+23 \\
    \hline
  \end{tabular}
\end{table*}

\begin{table*}
  \contcaption{LyC emissivities and the resultant hydrogen
    photoionisation rate due to quasars down to magnitudes
    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
    photoionisation rate calculation assumes an HI column density
    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
    further details.}
  \label{tab:gamma}
  \begin{tabular}{ccccc}
    \hline
    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
    \hline
    5.1 & 1.121e--13 & 3.758e--14 & 1.813e+24 & 6.963e+23 \\
    5.2 & 9.851e--14 & 3.222e--14 & 1.618e+24 & 6.129e+23 \\
    5.3 & 8.622e--14 & 2.752e--14 & 1.442e+24 & 5.387e+23 \\
    5.4 & 7.497e--14 & 2.333e--14 & 1.283e+24 & 4.728e+23 \\
    5.5 & 6.433e--14 & 1.952e--14 & 1.139e+24 & 4.143e+23 \\
    5.6 & 5.346e--14 & 1.579e--14 & 1.010e+24 & 3.626e+23 \\
    5.7 & 4.420e--14 & 1.269e--14 & 8.942e+23 & 3.169e+23 \\
    5.8 & 3.635e--14 & 1.014e--14 & 7.905e+23 & 2.766e+23 \\
    5.9 & 2.971e--14 & 8.054e--15 & 6.978e+23 & 2.412e+23 \\
    6.0 & 2.415e--14 & 6.354e--15 & 6.152e+23 & 2.100e+23 \\
    6.1 & 1.952e--14 & 4.982e--15 & 5.416e+23 & 1.826e+23 \\
    6.2 & 1.570e--14 & 3.883e--15 & 4.762e+23 & 1.587e+23 \\
    6.3 & 1.255e--14 & 3.004e--15 & 4.182e+23 & 1.377e+23 \\
    6.4 & 9.968e--15 & 2.310e--15 & 3.668e+23 & 1.193e+23 \\
    6.5 & 7.880e--15 & 1.766e--15 & 3.214e+23 & 1.033e+23 \\
    6.6 & 6.200e--15 & 1.343e--15 & 2.813e+23 & 8.940e+22 \\
    6.7 & 4.853e--15 & 1.015e--15 & 2.459e+23 & 7.726e+22 \\
    6.8 & 3.781e--15 & 7.634e--16 & 2.148e+23 & 6.670e+22 \\
    6.9 & 2.936e--15 & 5.721e--16 & 1.874e+23 & 5.753e+22 \\
    7.0 & 2.275e--15 & 4.277e--16 & 1.633e+23 & 4.958e+22 \\
    7.1 & 1.760e--15 & 3.192e--16 & 1.422e+23 & 4.269e+22 \\
    7.2 & 1.360e--15 & 2.379e--16 & 1.237e+23 & 3.672e+22 \\
    7.3 & 1.052e--15 & 1.775e--16 & 1.075e+23 & 3.156e+22 \\
    7.4 & 8.149e--16 & 1.327e--16 & 9.336e+22 & 2.710e+22 \\
    7.5 & 6.325e--16 & 9.947e--17 & 8.100e+22 & 2.326e+22 \\
    7.6 & 4.920e--16 & 7.477e--17 & 7.021e+22 & 1.994e+22 \\
    7.7 & 3.843e--16 & 5.645e--17 & 6.082e+22 & 1.709e+22 \\
    7.8 & 3.010e--16 & 4.278e--17 & 5.263e+22 & 1.463e+22 \\
    7.9 & 2.365e--16 & 3.253e--17 & 4.552e+22 & 1.251e+22 \\
    8.0 & 1.864e--16 & 2.483e--17 & 3.933e+22 & 1.070e+22 \\
    8.1 & 1.473e--16 & 1.902e--17 & 3.396e+22 & 9.138e+21 \\
    8.2 & 1.169e--16 & 1.462e--17 & 2.930e+22 & 7.800e+21 \\
    8.3 & 9.297e--17 & 1.128e--17 & 2.527e+22 & 6.654e+21 \\
    8.4 & 7.413e--17 & 8.725e--18 & 2.177e+22 & 5.673e+21 \\
    8.5 & 5.924e--17 & 6.767e--18 & 1.874e+22 & 4.833e+21 \\
    8.6 & 4.744e--17 & 5.260e--18 & 1.613e+22 & 4.115e+21 \\
    8.7 & 3.809e--17 & 4.100e--18 & 1.387e+22 & 3.502e+21 \\
    8.8 & 3.066e--17 & 3.205e--18 & 1.192e+22 & 2.978e+21 \\
    8.9 & 2.472e--17 & 2.510e--18 & 1.024e+22 & 2.531e+21 \\
    9.0 & 1.996e--17 & 1.969e--18 & 8.785e+21 & 2.149e+21 \\
    9.1 & 1.614e--17 & 1.547e--18 & 7.536e+21 & 1.825e+21 \\
    9.2 & 1.308e--17 & 1.218e--18 & 6.460e+21 & 1.548e+21 \\
    9.3 & 1.061e--17 & 9.604e--19 & 5.535e+21 & 1.313e+21 \\
    9.4 & 8.628e--18 & 7.588e--19 & 4.739e+21 & 1.112e+21 \\
    9.5 & 7.022e--18 & 6.002e--19 & 4.056e+21 & 9.423e+20 \\
    9.6 & 5.722e--18 & 4.753e--19 & 3.469e+21 & 7.978e+20 \\
    9.7 & 4.667e--18 & 3.769e--19 & 2.966e+21 & 6.751e+20 \\
    9.8 & 3.810e--18 & 2.991e--19 & 2.534e+21 & 5.709e+20 \\
    9.9 & 3.116e--18 & 2.377e--19 & 2.164e+21 & 4.826e+20 \\
    10.0 & 2.551e--18 & 1.892e--19 & 1.847e+21 & 4.078e+20 \\
    \hline
  \end{tabular}
\end{table*}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.6}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

\subsection{Hydrogen-ionizing emissivity}
\label{sec:e912}

@@

\subsection{Hydrogen photoionization rate}
\label{sec:gammahi}

@@

\section{Tables of emissivities and photoionisation rates}
\label{sec:tables}

Table~\ref{tab:emissivity_bins} shows the 912\,\AA\ and
1450\,\AA\ comoving emissivities obtained in various redshift bins
with the one-sigma (68.26\%) uncertainties.  Redshift bins severely
affected by systematic errors are also shown.  The result of the model
presented in Equation~(\ref{eqn:e912fit}), which describes the
emissivity evolution using a smooth function, is tabulated in
Table~\ref{tab:gamma2}, along with the hydrogen photoionization rate
computed in Section~\ref{sec:gammahi}.  In both tables, we show
results for our two integration limits of $M_{1450}<-18$ and
$M_{1450}<-21$.  These tables describe the curves shown in
Figures~\ref{fig:e912} and \ref{fig:gammapi}.  Note that the
photoionisation rate calculation assumes an \HI\ column density
distribution given by \citet{2012ApJ...746..125H} and extrapolates
this to high redshifts.

@@

    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.  Uncertainties
    are one-sigma (68.26\%).}

@@

  % rtg2.py and tabulate_emissivities_global.py.
  % Check these values once again.
  \caption{The 912\,\AA\ and 1450\,\AA\ comoving emissivities obtained
    by fitting Equation~(\ref{eqn:e912fit}) to the selected redshift
    bins from Table~\ref{tab:emissivity_bins}, and the corresponding
    hydrogen photoionisation rates with the one-sigma (68.26\%)
    uncertainties.  The emissivities are extrapolated here up to
    $z=15$.  Emissivity units are
    erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$, and photoionisation rate
    units are s$^{-1}$.  These values are shown in
    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  See
    Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.}
  \label{tab:gamma2}
  \begin{tabular}{d......}
    \multicolumn{1}{c}{$z$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} & 
    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} &
    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} \\ 
    0.0 & 23.36^{+0.38}_{-0.20} & 23.18^{+0.25}_{-0.22} & 23.01^{+0.23}_{-0.16} & 22.83^{+0.12}_{-0.15} & -13.38^{+0.10}_{-0.06} & -13.57^{+0.06}_{-0.05} \\
    0.1 & 23.54^{+0.29}_{-0.16} & 23.35^{+0.18}_{-0.17} & 23.24^{+0.18}_{-0.13} & 23.06^{+0.09}_{-0.11} & -13.22^{+0.08}_{-0.06} & -13.41^{+0.05}_{-0.04} \\
    0.2 & 23.71^{+0.21}_{-0.14} & 23.51^{+0.13}_{-0.12} & 23.45^{+0.14}_{-0.10} & 23.27^{+0.07}_{-0.09} & -13.07^{+0.06}_{-0.05} & -13.26^{+0.04}_{-0.03} \\
    0.3 & 23.85^{+0.16}_{-0.10} & 23.66^{+0.10}_{-0.08} & 23.64^{+0.10}_{-0.07} & 23.46^{+0.05}_{-0.06} & -12.94^{+0.05}_{-0.04} & -13.12^{+0.03}_{-0.03} \\
    0.4 & 23.99^{+0.11}_{-0.08} & 23.80^{+0.07}_{-0.06} & 23.81^{+0.07}_{-0.06} & 23.63^{+0.04}_{-0.04} & -12.82^{+0.04}_{-0.04} & -12.99^{+0.03}_{-0.02} \\
    0.5 & 24.11^{+0.08}_{-0.06} & 23.93^{+0.05}_{-0.04} & 23.95^{+0.05}_{-0.04} & 23.78^{+0.03}_{-0.03} & -12.71^{+0.03}_{-0.03} & -12.87^{+0.02}_{-0.02} \\
    0.6 & 24.23^{+0.05}_{-0.04} & 24.06^{+0.03}_{-0.02} & 24.09^{+0.04}_{-0.03} & 23.93^{+0.02}_{-0.02} & -12.60^{+0.03}_{-0.03} & -12.76^{+0.02}_{-0.02} \\
    0.7 & 24.34^{+0.03}_{-0.03} & 24.18^{+0.02}_{-0.02} & 24.21^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.51^{+0.03}_{-0.03} & -12.66^{+0.02}_{-0.02} \\
    0.8 & 24.44^{+0.03}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.32^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.42^{+0.03}_{-0.03} & -12.57^{+0.02}_{-0.02} \\
    0.9 & 24.54^{+0.02}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.02}_{-0.01} & 24.29^{+0.01}_{-0.01} & -12.35^{+0.02}_{-0.03} & -12.48^{+0.02}_{-0.02} \\
    1.0 & 24.63^{+0.02}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.02}_{-0.01} & 24.38^{+0.01}_{-0.01} & -12.28^{+0.02}_{-0.03} & -12.40^{+0.02}_{-0.02} \\
    1.1 & 24.71^{+0.02}_{-0.02} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.47^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.03} & -12.33^{+0.02}_{-0.02} \\
    1.2 & 24.78^{+0.02}_{-0.02} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.55^{+0.01}_{-0.01} & -12.16^{+0.03}_{-0.03} & -12.27^{+0.02}_{-0.02} \\
    1.3 & 24.85^{+0.01}_{-0.02} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.11^{+0.03}_{-0.03} & -12.22^{+0.02}_{-0.02} \\
    1.4 & 24.91^{+0.01}_{-0.02} & 24.82^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.18^{+0.02}_{-0.02} \\
    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.74^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
    1.6 & 24.99^{+0.02}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.02^{+0.03}_{-0.03} & -12.12^{+0.02}_{-0.02} \\
    1.7 & 25.03^{+0.02}_{-0.02} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.00^{+0.03}_{-0.03} & -12.11^{+0.02}_{-0.02} \\
    1.8 & 25.05^{+0.02}_{-0.02} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.02}_{-0.01} & 24.86^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.10^{+0.02}_{-0.02} \\
    1.9 & 25.07^{+0.02}_{-0.02} & 24.99^{+0.01}_{-0.01} & 24.96^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.09^{+0.03}_{-0.03} \\
    2.0 & 25.08^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.98^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.05} & -12.09^{+0.03}_{-0.03} \\
    2.1 & 25.09^{+0.03}_{-0.02} & 25.01^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.02} & 24.91^{+0.02}_{-0.02} & -11.99^{+0.05}_{-0.05} & -12.10^{+0.03}_{-0.03} \\
    2.2 & 25.09^{+0.03}_{-0.03} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.00^{+0.05}_{-0.06} & -12.11^{+0.04}_{-0.03} \\
    2.3 & 25.09^{+0.04}_{-0.04} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.03} & -12.01^{+0.05}_{-0.07} & -12.12^{+0.04}_{-0.04} \\
    2.4 & 25.08^{+0.04}_{-0.04} & 25.00^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.04} & 24.91^{+0.03}_{-0.03} & -12.03^{+0.06}_{-0.08} & -12.14^{+0.04}_{-0.04} \\
    2.5 & 25.07^{+0.04}_{-0.05} & 24.99^{+0.03}_{-0.03} & 25.01^{+0.04}_{-0.04} & 24.89^{+0.03}_{-0.04} & -12.04^{+0.06}_{-0.08} & -12.16^{+0.05}_{-0.05} \\
    2.6 & 25.06^{+0.05}_{-0.06} & 24.97^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.05} & 24.88^{+0.04}_{-0.04} & -12.06^{+0.07}_{-0.09} & -12.18^{+0.05}_{-0.05} \\
    2.7 & 25.04^{+0.05}_{-0.07} & 24.96^{+0.04}_{-0.04} & 25.00^{+0.05}_{-0.05} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.10} & -12.21^{+0.05}_{-0.05} \\
    2.8 & 25.02^{+0.06}_{-0.07} & 24.93^{+0.05}_{-0.04} & 24.99^{+0.06}_{-0.06} & 24.84^{+0.05}_{-0.04} & -12.11^{+0.07}_{-0.11} & -12.24^{+0.06}_{-0.06} \\
    2.9 & 25.01^{+0.06}_{-0.08} & 24.91^{+0.05}_{-0.05} & 24.98^{+0.06}_{-0.07} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.12} & -12.27^{+0.06}_{-0.06} \\
    3.0 & 24.98^{+0.06}_{-0.09} & 24.88^{+0.05}_{-0.05} & 24.96^{+0.06}_{-0.07} & 24.78^{+0.05}_{-0.05} & -12.17^{+0.08}_{-0.12} & -12.31^{+0.06}_{-0.07} \\
    3.1 & 24.96^{+0.07}_{-0.10} & 24.85^{+0.05}_{-0.06} & 24.94^{+0.07}_{-0.08} & 24.75^{+0.06}_{-0.05} & -12.20^{+0.09}_{-0.13} & -12.35^{+0.07}_{-0.07} \\
    3.2 & 24.93^{+0.07}_{-0.10} & 24.82^{+0.06}_{-0.06} & 24.91^{+0.07}_{-0.09} & 24.71^{+0.06}_{-0.05} & -12.23^{+0.09}_{-0.14} & -12.39^{+0.07}_{-0.08} \\
    3.3 & 24.91^{+0.08}_{-0.11} & 24.79^{+0.06}_{-0.06} & 24.89^{+0.08}_{-0.09} & 24.68^{+0.06}_{-0.06} & -12.26^{+0.10}_{-0.15} & -12.43^{+0.07}_{-0.08} \\
    3.4 & 24.88^{+0.08}_{-0.12} & 24.75^{+0.06}_{-0.07} & 24.86^{+0.08}_{-0.09} & 24.64^{+0.07}_{-0.06} & -12.30^{+0.10}_{-0.17} & -12.47^{+0.07}_{-0.09} \\
    3.5 & 24.85^{+0.09}_{-0.14} & 24.72^{+0.07}_{-0.07} & 24.83^{+0.08}_{-0.10} & 24.59^{+0.07}_{-0.06} & -12.34^{+0.11}_{-0.18} & -12.52^{+0.08}_{-0.09} \\
    3.6 & 24.82^{+0.10}_{-0.15} & 24.68^{+0.07}_{-0.08} & 24.80^{+0.09}_{-0.11} & 24.55^{+0.07}_{-0.06} & -12.38^{+0.11}_{-0.19} & -12.56^{+0.08}_{-0.10} \\
    3.7 & 24.79^{+0.10}_{-0.16} & 24.64^{+0.07}_{-0.08} & 24.77^{+0.09}_{-0.11} & 24.51^{+0.07}_{-0.06} & -12.42^{+0.12}_{-0.20} & -12.61^{+0.08}_{-0.10} \\
    3.8 & 24.75^{+0.10}_{-0.16} & 24.59^{+0.07}_{-0.09} & 24.73^{+0.10}_{-0.12} & 24.47^{+0.07}_{-0.07} & -12.46^{+0.12}_{-0.21} & -12.66^{+0.08}_{-0.11} \\
    3.9 & 24.72^{+0.11}_{-0.17} & 24.55^{+0.07}_{-0.09} & 24.70^{+0.10}_{-0.13} & 24.42^{+0.07}_{-0.07} & -12.50^{+0.13}_{-0.22} & -12.72^{+0.08}_{-0.11} \\
    4.0 & 24.68^{+0.11}_{-0.18} & 24.51^{+0.07}_{-0.09} & 24.66^{+0.10}_{-0.14} & 24.37^{+0.07}_{-0.08} & -12.54^{+0.13}_{-0.24} & -12.77^{+0.08}_{-0.12} \\
    4.1 & 24.65^{+0.11}_{-0.20} & 24.46^{+0.07}_{-0.10} & 24.63^{+0.11}_{-0.16} & 24.33^{+0.06}_{-0.09} & -12.58^{+0.13}_{-0.25} & -12.82^{+0.08}_{-0.12} \\
    4.2 & 24.61^{+0.12}_{-0.21} & 24.42^{+0.07}_{-0.10} & 24.58^{+0.12}_{-0.16} & 24.28^{+0.06}_{-0.10} & -12.63^{+0.14}_{-0.27} & -12.88^{+0.08}_{-0.12} \\
    4.3 & 24.58^{+0.13}_{-0.23} & 24.37^{+0.07}_{-0.11} & 24.54^{+0.12}_{-0.17} & 24.23^{+0.07}_{-0.10} & -12.67^{+0.14}_{-0.29} & -12.94^{+0.09}_{-0.13} \\
    4.4 & 24.54^{+0.12}_{-0.24} & 24.32^{+0.08}_{-0.11} & 24.50^{+0.13}_{-0.18} & 24.17^{+0.07}_{-0.11} & -12.72^{+0.14}_{-0.30} & -13.00^{+0.09}_{-0.13} \\
    4.5 & 24.50^{+0.13}_{-0.26} & 24.27^{+0.08}_{-0.11} & 24.45^{+0.14}_{-0.19} & 24.12^{+0.07}_{-0.12} & -12.76^{+0.15}_{-0.32} & -13.06^{+0.09}_{-0.14} \\
    4.6 & 24.46^{+0.13}_{-0.28} & 24.22^{+0.08}_{-0.12} & 24.40^{+0.15}_{-0.19} & 24.07^{+0.08}_{-0.12} & -12.81^{+0.15}_{-0.34} & -13.12^{+0.10}_{-0.14} \\
    4.7 & 24.42^{+0.14}_{-0.30} & 24.16^{+0.09}_{-0.12} & 24.36^{+0.16}_{-0.21} & 24.01^{+0.08}_{-0.13} & -12.86^{+0.16}_{-0.36} & -13.18^{+0.11}_{-0.14} \\
    4.8 & 24.38^{+0.15}_{-0.31} & 24.11^{+0.09}_{-0.13} & 24.31^{+0.17}_{-0.22} & 23.96^{+0.09}_{-0.14} & -12.91^{+0.17}_{-0.38} & -13.25^{+0.11}_{-0.15} \\
    4.9 & 24.34^{+0.15}_{-0.33} & 24.05^{+0.10}_{-0.13} & 24.26^{+0.17}_{-0.24} & 23.90^{+0.09}_{-0.15} & -12.96^{+0.18}_{-0.39} & -13.32^{+0.12}_{-0.15} \\
    5.0 & 24.30^{+0.16}_{-0.35} & 23.99^{+0.11}_{-0.13} & 24.21^{+0.17}_{-0.25} & 23.84^{+0.10}_{-0.17} & -13.01^{+0.19}_{-0.41} & -13.38^{+0.13}_{-0.16} \\
  \contcaption{}
  \begin{tabular}{d......}
    \multicolumn{1}{c}{$z$} &    
    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} &
    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} & 
    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} &
    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} \\ 
    5.1 & 24.26^{+0.17}_{-0.36} & 23.93^{+0.11}_{-0.14} & 24.16^{+0.18}_{-0.26} & 23.78^{+0.10}_{-0.19} & -13.06^{+0.20}_{-0.42} & -13.45^{+0.13}_{-0.16} \\
    5.2 & 24.21^{+0.19}_{-0.37} & 23.88^{+0.12}_{-0.14} & 24.10^{+0.19}_{-0.27} & 23.72^{+0.11}_{-0.20} & -13.12^{+0.21}_{-0.44} & -13.52^{+0.14}_{-0.17} \\
    5.3 & 24.17^{+0.20}_{-0.39} & 23.82^{+0.13}_{-0.15} & 24.05^{+0.19}_{-0.29} & 23.66^{+0.12}_{-0.22} & -13.17^{+0.22}_{-0.46} & -13.59^{+0.15}_{-0.18} \\
